### 2021-02-24 architecture.tex
Improve wording of a paragraph

To train a useful symbol cost function $c$,
we define a precedence cost function $C$ on top of $c$
in a way that ensures that minimizing $C$ corresponds to sorting the symbols by $c$,
so that finding the precedence that minimizes $C$ can be done efficiently and precisely.
Then we proceed to train $C$ on the proxy task of ranking the precedences.

>>>>

To train a useful symbol cost function $c$,
we define a precedence cost function $C$ using the symbol cost function $c$
in a manner than ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
Finding the precedence that minimizes $C$ can then be done efficiently and precisely.
We proceed to train $C$ on the proxy task of ranking the precedences.
